---
title: "R Notebook"
output: html_notebook
---
Load libraries

```{r}
library(readr)
library(tidyverse)
library(survival)
library(ggfortify)
library(ranger)
library(survminer)
library(stargazer)
```

Now, bio calibration data

```{r}
basePath = "C:/dev/EconABM/Analysis/survival_analysis/bio_calibrate_files"
#65
df = data.frame(X1=numeric(),t=numeric(), groveID=character(), E=logical(), strategy=character(), alpha=numeric())
for (efficacy in c(65,75,85)) {
  path = paste(basePath,"/",efficacy,sep="")
  setwd(path)
  e_df = list.files(path, pattern="*.csv") %>% map_df(~read_csv(.))
  e_df$efficacy = (efficacy / 100)
  df = rbind(df,e_df)
}

df = df %>% select(t, groveID, E, efficacy, strategy, alpha)
#Grab a few more from window pairs to round it out
ga_ac_65 = read.csv("C:/dev/EconABM/Analysis/survival_analysis/windowPairs/w21_e65.csv")
ga_ac_75 = read.csv("C:/dev/EconABM/Analysis/survival_analysis/windowPairs/w21_e75.csv")
ga_ac_85 = read.csv("C:/dev/EconABM/Analysis/survival_analysis/windowPairs/w21_e85.csv")
combined = rbind(ga_ac_65,ga_ac_75,ga_ac_85) %>% select(t, groveID, E, efficacy)
combined$strategy = "Group Action"
combined$alpha = 1
combined$E = as.logical(combined$E)
df = rbind(df, combined) 

df$groveID = as.factor(df$groveID)
df$alpha = as.factor(df$alpha)
df$strategy = as.factor(df$strategy)
df$strategy = factor(df$strategy, levels=c("No Action", "Individual Action", "Group Action"))
```


```{r}
stargazer(as.data.frame(df %>% select(t, E, efficacy, strategy, alpha)),
          type="latex", 
          summary.stat = c("n","sd","mean", "min", "max"),
          title="Summary of Variable Coordination Data",
          label="Tab:varcoord-summary")
```

Plot stratified KM curves

```{r}
alphas = c(0,1)
efficacies = c(0.65,0.75,0.85)
strategies = c("Individual Action", "No Action", "Group Action")

ggDF = data.frame(Time=integer(), Surv=double(), CumHaz=double(), Hazard=double(), Efficacy=double(), Window=integer())
for (a in alphas) {
  for (s in strategies) {
    for (e in efficacies) {
      km = df %>% filter (efficacy == e, strategy == s, alpha == a)
      km = survfit(Surv(t,E) ~ 1, data=km)
      hazardtable = broom::tidy(km) %>% filter(n.event > 0) %>% mutate(hazard = n.event / (n.risk * (lead(time) - time)))
      km_df = data.frame(time=km$time, 
                         Surv=km$surv, 
                         CumHaz=km$cumhaz, 
                         Efficacy=rep(e, length(km$time)), 
                         Strategy=rep(s, length(km$time)),
                         Alpha=rep(a, length(km$time)))
      km_df = left_join(km_df, hazardtable, by=c("time"))
      km_df = km_df %>% select(time, Surv, CumHaz, hazard, Efficacy, Strategy, Alpha)
      names(km_df) =  c("Time", "Surv", "CumHaz", "Hazard", "Efficacy", "Strategy", "Alpha")
      ggDF = rbind(ggDF, km_df)
      
    }
    
   
  }
}

ggDF$Efficacy = as.factor(ggDF$Efficacy)
ggDF$Alpha = as.factor(ggDF$Alpha)
ggDF$Strategy = factor(ggDF$Strategy, levels= c("No Action", "Individual Action", "Group Action"))
```

```{r}
gg_65 = ggDF %>%
  filter(Efficacy==0.65) %>%
  ggplot(aes(x=Time, y=Surv, color=Strategy, linetype=Alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")

gg_75 = ggDF %>%
  filter(Efficacy==0.75) %>%
  ggplot(aes(x=Time, y=Surv, color=Strategy, linetype=Alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")


gg_85 = ggDF %>%
  filter(Efficacy==0.85) %>%
  ggplot(aes(x=Time, y=Surv, color=Strategy, linetype=Alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")


gg_65
ggsave("biocalibrate-output/survivalMean65.png", width = 7, height=5, dpi=300)
gg_75
ggsave("biocalibrate-output/survivalMean75.png", width = 7, height=5, dpi=300)
gg_85
ggsave("biocalibrate-output/survivalMean85.png", width = 7, height=5, dpi=300)
```

Time to test models


First testing a baseline cox model with all the variables
```{r}
df$efficacy = as.factor(df$efficacy)
combos = data.frame(model=character(), AIC_I=double())
coxfit = coxph(Surv(t,E) ~ strategy + efficacy*alpha  + groveID, data=df)
summary(coxfit)
extractAIC(coxfit)
combos = combos %>% add_row(model="cox", AIC_I=extractAIC(coxfit)[2])
```

And now each of the standard distributions included with the package. First with interaction term
```{r}

for (dis in c("weibull", "exponential", "gaussian","logistic","lognormal","loglogistic")) {
  print(dis)
  fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha  + groveID, data=df, dist=dis)
  print(summary(fit))
  print(extractAIC(fit))
  combos = combos %>% add_row(model=dis, AIC_I = extractAIC(fit)[2])
}
```
```{r}
w_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID, data=df, dist="weibull")
e_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID, data=df, dist="exponential")
g_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID, data=df, dist="gaussian")
l_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID, data=df, dist="logistic")
ln_fit = survreg(Surv(t,E) ~strategy + efficacy*alpha + groveID, data=df, dist="lognormal")
ll_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID, data=df, dist="loglogistic")
stargazer(w_fit,e_fit,g_fit,l_fit,ln_fit,ll_fit, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          float.env = "sidewaystable",
          title="Interaction bio-calibrate",
          column.labels = c("Weibull", "Exponential", "Gaussian", "Logistic", "Lognormal", "Loglogistic"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```
Compare AIC across models
```{r}
print(combos)

```

The data seems to suggest that at higher efficacies and complete cooperation, spraying strategies have more influence. Let's try again with a 3 way interaction term we add by hand, as well as an interaction between alpha and efficacy
```{r}
df$threeterm = if_else(df$alpha == 1 & df$efficacy==0.85 & df$strategy!="No Action", TRUE, FALSE)
combos = data.frame(model=character(), AIC_I=double())
coxfit = coxph(Surv(t,E) ~ strategy + efficacy*alpha  + groveID + threeterm, data=df)
summary(coxfit)
extractAIC(coxfit)
combos = combos %>% add_row(model="cox", AIC_I=extractAIC(coxfit)[2])
```

And now each of the standard distributions included with the package. First with interaction term
```{r}

for (dis in c("weibull", "exponential", "gaussian","logistic","lognormal","loglogistic")) {
  print(dis)
  fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha  + groveID + threeterm, data=df, dist=dis)
  print(summary(fit))
  print(extractAIC(fit))
  combos = combos %>% add_row(model=dis, AIC_I = extractAIC(fit)[2])
}
```

```{r}
w_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID + threeterm, data=df, dist="weibull")
e_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID + threeterm, data=df, dist="exponential")
g_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID + threeterm, data=df, dist="gaussian")
l_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID + threeterm, data=df, dist="logistic")
ln_fit = survreg(Surv(t,E) ~strategy + efficacy*alpha + groveID + threeterm, data=df, dist="lognormal")
ll_fit = survreg(Surv(t,E) ~ strategy + efficacy*alpha + groveID + threeterm, data=df, dist="loglogistic")
stargazer(w_fit,e_fit,g_fit,l_fit,ln_fit,ll_fit, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          float.env = "sidewaystable",
          title="Threeterm bio-calibrate",
          column.labels = c("Weibull", "Exponential", "Gaussian", "Logistic", "Lognormal", "Loglogistic"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```

Compare AIC across models
```{r}
print(combos)
```


Three term weibull seemed to be the best, let's look closer
```{r}
wfit = survreg(Surv(t,E) ~ strategy + efficacy*alpha  + groveID, data=df, dist="weibull")
wfit_t = survreg(Surv(t,E) ~ strategy + efficacy*alpha  + groveID + threeterm, data=df, dist="weibull")
stargazer(wfit,wfit_t, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          title="weibull comparison",
          column.labels = c("Weibull(Interaction)", "Weibull(\textttt{threeterm})"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```
Check out exponentiated coefficients
```{r}
cbind(coef(wfit), "exp(coef)"=exp(coef(wfit)), confint(wfit))
```
Checking prediction
```{r}
nd1 = data.frame(alpha=factor(0, levels=c(0,1)),
                 efficacy=factor(0.75, levels=c(0.65,0.75,0.85)),
                 strategy=factor("No Action", levels=c("No Action", "Individual Action", "Group Action")),
                 groveID=factor("g01", levels=c("g00","g01","g02","g10","g11","g12","g20","g21","g22")),
                 threeterm=FALSE)
nd2 = data.frame(alpha=factor(1, levels=c(0,1)),
                 efficacy=factor(0.75, levels=c(0.65,0.75,0.85)),
                 strategy=factor("No Action", levels=c("No Action", "Individual Action", "Group Action")),
                 groveID=factor("g01", levels=c("g00","g01","g02","g10","g11","g12","g20","g21","g22")),
                 threeterm=FALSE)

predict(wfit, newdata=nd2) / predict(wfit, newdata=nd1)
```
Confirmed, coefficient interpretation can be done by exponentiating the change in the linear model, which is the % increase in survival time

```{r}
predictionData = data.frame(t=numeric(), strategy=character(), alpha=numeric(), groveID=character(), efficacy=numeric(), threeterm=logical())
for (e in c(0.65,0.75,0.85)) {
  for (s in c("No Action", "Individual Action", "Group Action")) {
    for (gID in c("g00", "g01", "g02", "g10", "g11", "g12", "g20", "g21", "g22")) {
      for (a in c(0,1)) {
        loopThree = (e == 0.85 && s != "No Action" && a==1)
        loopDF = data.frame(t=seq(0,1825), strategy=s, alpha=a, groveID=gID, efficacy=e, threeterm=loopThree)
        predictionData=rbind(predictionData,loopDF)
      }
    }
  }
}
predictionData$strategy = factor(predictionData$strategy, levels=c("No Action", "Individual Action", "Group Action"))
predictionData$alpha = as.factor(predictionData$alpha)
predictionData$efficacy = as.factor(predictionData$efficacy)
predictionData$survival_lp = predict(wfit, newdata=predictionData,type="lp")
predictionData$survival = exp(-1 * ((predictionData$t / exp(predictionData$survival_lp))^(1/wfit$scale)))
```

```{r}
ggPD = predictionData %>% group_by(t, strategy, alpha, efficacy) %>% summarize(survival = mean(survival))
gg_65 = ggPD %>%
  filter(efficacy==0.65) %>%
  ggplot(aes(x=t, y=survival, color=strategy, linetype=alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")

gg_75 = ggPD %>%
  filter(efficacy==0.75) %>%
  ggplot(aes(x=t, y=survival, color=strategy, linetype=alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")

gg_85 = ggPD %>%
  filter(efficacy==0.85) %>%
  ggplot(aes(x=t, y=survival, color=strategy, linetype=alpha)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  labs(color="Strategy", linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")


gg_65
ggsave("biocalibrate-output/survivalPrediction65.png", width = 7, height=5, dpi=300)
gg_75
ggsave("biocalibrate-output/survivalPrediction75.png", width = 7, height=5, dpi=300)
gg_85
ggsave("biocalibrate-output/survivalPrediction85.png", width = 7, height=5, dpi=300)

```

