---
title: "R Notebook"
output: html_notebook
---

Load libraries

```{r}
library(readr)
library(tidyverse)
library(survival)
library(ggfortify)
library(ranger)
library(survminer)
library(stargazer)
library(viridis)
```
FIRST, WINDOW PAIRS

Gather files

```{r message = FALSE}
basePath = "C:/dev/EconABM/Analysis/survival_analysis/windowPairs-all"
setwd(basePath)
df = list.files(basePath, pattern="*.csv") %>% map_df(~read_csv(.))
df$groveID = as.factor(df$groveID)
```

```{r}
stargazer(as.data.frame(df %>% select(t, E, window, efficacy)),
          type="latex", 
          summary.stat = c("n","sd","mean", "min", "max"),
          title="Summary of Full Coordination Data")
```


Plot stratified KM curves

```{r}
windows = c(7,14,21,40,60,80,100)
efficacies = c(0.65,0.75,0.85)

ggDF = data.frame(Time=integer(), Surv=double(), CumHaz=double(), Hazard=double(), Efficacy=double(), Window=integer())
for (w in windows) {
  for (e in efficacies) {
    km = df %>% filter (efficacy == e, window == w)
    km = survfit(Surv(t,E) ~ 1, data=km)
    hazardtable = broom::tidy(km) %>% filter(n.event > 0) %>% mutate(hazard = n.event / (n.risk * (lead(time) - time)))
    km_df = data.frame(time=km$time, Surv=km$surv, CumHaz=km$cumhaz, Efficacy=rep(e, length(km$time)), Window=rep(w, length(km$time)))
    km_df = left_join(km_df, hazardtable, by=c("time"))
    km_df = km_df %>% select(time, Surv, CumHaz, hazard, Efficacy, Window)
    names(km_df) =  c("Time", "Surv", "CumHaz", "Hazard", "Efficacy", "Window")
    ggDF = rbind(ggDF, km_df)
  }
}

ggDF$Efficacy = as.factor(ggDF$Efficacy)
ggDF$Window = as.factor(ggDF$Window)

```

```{r}
ggDF %>%
  ggplot(aes(x=Time, y=Surv, color=Efficacy, linetype=Window)) +
  geom_line() +
  xlab("Days since start of simulation") +
  ylab("Survival Probability") +
  scale_color_viridis(discrete=TRUE, option="turbo")
ggsave("windowpairs-output/windowPairsSurvival.png", dpi=300, width=7, height=5)

```
Cumulative Hazard plots
```{r}
ggDF %>%
  ggplot(aes(x=Time, y=CumHaz, color=Efficacy, linetype=Window)) +
  geom_line()

```

Hazard plots
```{r}
oneLine = ggDF %>% filter(Efficacy==0.85, Window==7) 
ggDF %>%
  filter(Efficacy==0.85, Window==7) %>%
  ggplot(aes(x=Time, y=Hazard, color=Efficacy)) +
  geom_point()
```



And now analysis. First testing a baseline cox model
```{r}
combos = data.frame(model=character(), AIC_I=double())
coxfit = coxph(Surv(t,E) ~ window + efficacy + window*efficacy + groveID, data=df)
summary(coxfit)
extractAIC(coxfit)
combos = combos %>% add_row(model="cox", AIC_I=extractAIC(coxfit)[2])
```

And now each of the standard distributions included with the package. First with interaction term
```{r}

for (dis in c("weibull", "exponential", "gaussian","logistic","lognormal","loglogistic")) {
  print(dis)
  fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist=dis)
  print(summary(fit))
  print(extractAIC(fit))
  combos = combos %>% add_row(model=dis, AIC_I = extractAIC(fit)[2])
}
```
```{r}
df$efficacy = as.factor(df$efficacy)
w_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="weibull")
e_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="exponential")
g_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="gaussian")
l_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="logistic")
ln_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="lognormal")
ll_fit = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="loglogistic")
stargazer(w_fit,e_fit,g_fit,l_fit,ln_fit,ll_fit, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          float.env = "sidewaystable",
          title="Window Pair Interaction",
          column.labels = c("Weibull", "Exponential", "Gaussian", "Logistic", "Lognormal", "Loglogistic"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)

```
Compare AIC across models
```{r}
print(combos)

```
 
 
 
 again without interaction term
```{r}
combos_ni = data.frame(model=character(), AIC_NI=double())
coxfit = coxph(Surv(t,E) ~ window + efficacy + groveID, data=df)
summary(coxfit)
extractAIC(coxfit)
combos_ni = combos_ni %>% add_row(model="cox", AIC_NI=extractAIC(coxfit)[2])
```
```{r}

for (dis in c("weibull", "exponential", "gaussian","logistic","lognormal","loglogistic")) {
  print(dis)
  fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist=dis)
  print(summary(fit))
  print(extractAIC(fit))
  combos_ni = combos_ni %>% add_row(model=dis, AIC_NI=extractAIC(fit)[2])
}
```
```{r}
w_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="weibull")
e_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="exponential")
g_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="gaussian")
l_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="logistic")
ln_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="lognormal")
ll_fit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="loglogistic")
stargazer(w_fit,e_fit,g_fit,l_fit,ln_fit,ll_fit, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          float.env = "sidewaystable",
          title="Window Pair Linear",
          column.labels = c("Weibull", "Exponential", "Gaussian", "Logistic", "Lognormal", "Loglogistic"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```
```{r}
aic_table = left_join(combos, combos_ni, by=c("model"))
print(aic_table)
```


Since the best model is weibull let's look more closely
```{r}
df$efficacy = as.factor(df$efficacy)
wfit = survreg(Surv(t,E) ~ efficacy + window + groveID, data=df, dist="weibull")
wfit_i = survreg(Surv(t,E) ~ efficacy + window + window*efficacy + groveID, data=df, dist="weibull")
stargazer(wfit,wfit_i, 
          align=TRUE, omit=c("groveID*"), no.space=TRUE,
          title="Weibull regression output for full coordination specifications",
          label="Tab:windowPair-coeff-interaction",
          column.labels = c("Weibull(Linear)", "Weibull(Interaction)"),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)

```