---
title: "R Notebook"
output: html_notebook
---


BIO CALIBRATE EV ANALYSIS

This file contains the analysis required for testing the effects of strategy and alpha on in grove spread.




Load required libraries
```{r}
library(tidyverse)
library(dbplyr)
library(betareg)
library(stargazer)
library(viridis)
```

Data available in the database in the table "biocalibrate_ev_import", but I use a local file for speed purposes
```{r}
df = read.csv("C:/dev/biocalibrate-ev-legacy.csv")
```

```{r}
gg65 = 
  df %>%
    mutate(efficacy=as.factor(efficacy), 
           strategy=factor(strategy, levels=c("No Action", "Individual Action", "Group Action")),
           alpha=as.factor(alpha)) %>%
    filter(efficacy==0.65) %>%
    group_by(strategy,alpha,relT) %>%
    summarize(hlb = mean(hlbSeverity)) %>%
  ggplot(aes(x=relT,y=hlb,color=strategy,linetype=alpha)) +
  geom_line() +
  scale_y_continuous(breaks=seq(0,1,0.1)) +
  labs(x="Days Since Initial Infection",
       y="Mean Severity",
       color="Strategy",
       linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")
gg65
ggsave("biocalibrate-output/meanSpread_65.png", dpi=300, width=7, height=5)
gg75 = 
  df %>%
    mutate(efficacy=as.factor(efficacy), 
           strategy=factor(strategy, levels=c("No Action", "Individual Action", "Group Action")),
           alpha=as.factor(alpha)) %>%
    filter(efficacy==0.75) %>%
    group_by(strategy,alpha,relT) %>%
    summarize(hlb = mean(hlbSeverity)) %>%
  ggplot(aes(x=relT,y=hlb,color=strategy,linetype=alpha)) +
  geom_line() +
  scale_y_continuous(breaks=seq(0,1,0.1)) +
  labs(x="Days Since Initial Infection",
       y="Mean Severity",
       color="Strategy",
       linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")
gg75
ggsave("biocalibrate-output/meanSpread_75.png", dpi=300, width=7, height=5)
gg85 = 
  df %>%
    mutate(efficacy=as.factor(efficacy), 
           strategy=factor(strategy, levels=c("No Action", "Individual Action", "Group Action")),
           alpha=as.factor(alpha)) %>%
    filter(efficacy==0.85) %>%
    group_by(strategy,alpha,relT) %>%
    summarize(hlb = mean(hlbSeverity)) %>%
  ggplot(aes(x=relT,y=hlb,color=strategy,linetype=alpha)) +
  geom_line() +
  scale_y_continuous(breaks=seq(0,1,0.1)) +
  labs(x="Days Since Initial Infection",
       y="Mean Severity",
       color="Strategy",
       linetype="Alpha") +
  scale_color_viridis(discrete=TRUE, option="turbo")
gg85
ggsave("biocalibrate-output/meanSpread_85.png", dpi=300, width=7, height=5)
```


Change format for max value estimation
```{r}
df = df %>%
      mutate(zeroes=relT == 0,
             pid = cumsum(zeroes)) %>%
      group_by(pid) %>%
      summarize(maxHLB = max(hlbSeverity), maxT = max(relT), efficacy=max(efficacy), 
                strategy=max(strategy), alpha=max(alpha))
```

Factor conversion
```{r}
df$efficacy = as.factor(df$efficacy)
df$alpha = as.factor(df$alpha)
df$strategy = factor(df$strategy, levels=c("No Action", "Individual Action", "Group Action"))
```

Since response variable is bound on [0,1], we use a beta regression for estimation. We test the 3 different estimators available: maximum likelihood, bias correction, bias reduction. Throw in an OLS for shiggles

```{r}
fm = maxHLB ~ efficacy*alpha + efficacy*strategy*maxT
ols = lm(fm, data=df)
br.ml = betareg(fm, data=df, type="ML")
br.bc = betareg(fm, data=df, type="BC")
br.br = betareg(fm, data=df, type="BR")
```

Comparing 3 models
```{r}
stargazer(ols, br.ml,br.bc,br.br, 
          type="text",
          title="Regression output for variable coordination model",
          label="Tab:ExpectedValue-BioCalibrate-regressionoutput",
          font.size = "tiny",
          column.labels = c("OLS", "ML", "BC", "BR"),
          add.lines=list(
            c("AIC", round(AIC(ols),digits=5), round(AIC(br.ml),digits=5), round(AIC(br.bc),digits=5), round(AIC(br.br),digits=5)),
            c("BIC", round(BIC(ols),digits=5), round(BIC(br.ml),digits=5), round(BIC(br.bc),digits=5), round(BIC(br.br),digits=5))
            ),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```

Inference is done with graphs

```{r}
predictionData = data.frame(maxT=rep(1:3650,18), 
                            strategy=rep(c("No Action", "Individual Action", "Group Action"),1, each=3650*6), 
                            efficacy=rep(c(0.65,0.75,0.85),3, each=3650*2), 
                            alpha=rep(0:1,9, each=3650))
predictionData =
  predictionData %>% 
  mutate(strategy=factor(strategy, levels=c("No Action", "Individual Action", "Group Action")),
         efficacy=as.factor(efficacy),
         alpha=as.factor(alpha))
predictionData$maxHLB = predict(br.ml, predictionData)
```


```{r}
p65 = 
  predictionData %>%
    filter(efficacy==0.65) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=maxHLB, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Severity",
         color="Strategy",
         linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +
    scale_color_viridis(discrete=TRUE, option="turbo")


p75 = 
  predictionData %>%
    filter(efficacy==0.75) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=maxHLB, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Severity",
         color="Strategy", linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +        
    scale_color_viridis(discrete=TRUE, option="turbo")




p85 = 
  predictionData %>%
    filter(efficacy==0.85) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=maxHLB, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Severity",
         color="Strategy", linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +
    scale_color_viridis(discrete=TRUE, option="turbo")



p65
ggsave("biocalibrate-output/predictedSpread_65.png", dpi=300, width=7, height=5)
p75
ggsave("biocalibrate-output/predictedSpread_75.png", dpi=300, width=7, height=5)
p85
ggsave("biocalibrate-output/predictedSpread_85.png", dpi=300, width=7, height=5)

```


yield curves
```{r}
predictionData$yield = exp(-1.85*predictionData$maxHLB)
```


```{r}
p65 = 
  predictionData %>%
    filter(efficacy==0.65) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=yield, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Yield",
         color="Strategy", linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +
    scale_color_viridis(discrete=TRUE, option="turbo")




p75 = 
  predictionData %>%
    filter(efficacy==0.75) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=yield, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Yield", 
         color="Strategy", linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +
    scale_color_viridis(discrete=TRUE, option="turbo")




p85 = 
  predictionData %>%
    filter(efficacy==0.85) %>%
    mutate(year=maxT/365) %>%
    ggplot(aes(x=year, y=yield, color=strategy, linetype=alpha)) +
    geom_line() +
    labs(
         x="Years of Infection", y="Yield",
         color="Strategy", linetype="Alpha") +
    scale_y_continuous(breaks=seq(0,1,0.1)) +
    scale_x_continuous(breaks=seq(0,10,1)) +
    scale_color_viridis(discrete=TRUE, option="turbo")




p65
ggsave("biocalibrate-output/predictedYield_65.png", dpi=300, width=7, height=5)
p75
ggsave("biocalibrate-output/predictedYield_75.png", dpi=300, width=7, height=5)
p85
ggsave("biocalibrate-output/predictedYield_85.png", dpi=300, width=7, height=5)
```


```{r}
predictionData = predictionData %>% filter(maxT <= 1825)
premiumDF_indv = predictionData %>% 
                 filter(efficacy == 0.85 & strategy == 'Individual Action') %>% 
                 group_by(maxT,alpha) %>%
                 summarize(indvYield = mean(yield))
premiumDF_group = predictionData %>% 
                 filter(efficacy == 0.85 & strategy == 'Group Action') %>% 
                 group_by(maxT,alpha) %>%
                 summarize(groupYield = mean(yield))
premiumDF_none = predictionData %>% 
                 filter(efficacy == 0.85 & strategy == 'No Action') %>% 
                 group_by(maxT,alpha) %>%
                 summarize(noneYield = mean(yield))
premiumDF = left_join(premiumDF_group, premiumDF_indv, by=c("maxT", "alpha"))
premiumDF_extra = left_join(premiumDF, premiumDF_none, by=c("maxT", "alpha"))
```

```{r}
premiumDF_extra = premiumDF_extra %>% mutate(yieldDiff = groupYield - indvYield, noneDiff = groupYield - noneYield)
premiumDF_extra %>% 
  ggplot(aes(x=maxT, y=yieldDiff, linetype=alpha)) +
  geom_line(color="green") +
  geom_line(aes(x=maxT, y=noneDiff, linetype=alpha), color="red")
```

Now that we have yield difference curves for alpha values, we want the mean duration of infections
```{r}
 wrangled = premiumDF_extra %>% 
  filter((maxT %% 365) == 100 | (maxT %% 365) == 200 | (maxT %% 365) == 300) %>%
  mutate(harvest = cumsum(yieldDiff), harvestNone=cumsum(noneDiff)) %>% 
  group_by(alpha) %>%
  filter(maxT == max(maxT)) %>% 
  select(harvest, harvestNone)

alpha0Diff = wrangled$harvest[1]
alpha1Diff = wrangled$harvest[2]
alpha0NoneDiff = wrangled$harvestNone[1]
alpha1NoneDiff = wrangled$harvestNone[2]




```
```{r}
fruitPrice = 17.60
fruitYield = 237.14

alpha0Loss = fruitPrice * fruitYield * alpha0Diff
alpha1Loss = fruitPrice * fruitYield * alpha1Diff
alpha0NoneLoss = fruitPrice * fruitYield * alpha0NoneDiff
alpha1NoneLoss = fruitPrice * fruitYield * alpha1NoneDiff
meanLoss = (alpha0Loss + alpha1Loss) / 2
groupPremium = meanLoss / 6 / 5
groupPremium
meanNoneLoss = (alpha0NoneLoss + alpha1NoneLoss) / 2
sprayPremium = meanNoneLoss / 6 / 5

print(paste("Group vs Indv Loss (alpha 0) per year:",alpha0Loss / 5))
print(paste("Group vs Indv Loss (alpha 1) per year:",alpha1Loss / 5))
print(paste("Group vs Indv Loss average per year:", ((alpha1Loss / 5) + (alpha0Loss / 5)) / 2))
print(paste("Group vs No Action Loss (alpha 0) per year:",alpha0NoneLoss / 5))
print(paste("Group vs No Action Loss (alpha 1) per year:",alpha1NoneLoss / 5))
print(paste("Group vs No Action Average per year", ((alpha1NoneLoss / 5) + (alpha0NoneLoss / 5)) / 2))
print(paste("Group Premium vs indv (per spray):", groupPremium))
print(paste("Group gains vs none(per spray):", sprayPremium))


```







