---
title: "R Notebook"
output: html_notebook
---

WINDOW PAIR EV ANALYSIS

This file contains the analysis required for testing the effects of window and efficacy on in grove spread.




Load required libraries
```{r}
library(tidyverse)
library(dbplyr)
library(betareg)
library(stargazer)
```


Data is contained in the database @ "windowpairs_ev_import", but im gonna use a local file here for convenience


Labeller helper func
```{r}
niceLabeller = function(variable, value) {
  fixedvar = str_to_title(gsub("_", " ", variable))
  full = paste(fixedvar, ": ", value, sep="")
}

```
Manipulate data and bring it down for local modelling. Change efficacy to factor.
```{r}
df = read.csv("C:/dev/windowPairslegacy.csv")
```

```{r}
df %>%
  mutate(efficacy=as.factor(efficacy), window=as.factor(window)) %>%
  group_by(window,efficacy, relT) %>%
  summarize(hlb=mean(adjustedSeverity)) %>%
  ggplot(aes(x=relT,y=hlb, color=efficacy, linetype=window)) +
  geom_line() + 
  labs(
       y="Mean HLB Severity", 
       x="Days Since Initial Infection",
       color="Efficacy",
       linetype="Window") +
  scale_y_continuous(breaks=seq(0,1,by=0.1)) +
  scale_color_viridis(discrete=TRUE, option="turbo") +
  theme_grey()
ggsave("windowpairs-output/meanSpread.jpg", dpi=300, width=7, height=5)
```

Transform in use with max EV models
```{r}
df = df %>%
      group_by(pid) %>%
      summarize(maxHLB=max(adjustedSeverity),
                efficacy=max(efficacy),
                window=max(window),
                maxT=max(relT)
                ) %>%
      mutate(efficacy=as.factor(efficacy))
```

Since response variable is bound on [0,1], we use a beta regression for estimation. We test the 3 different estimators available: maximum likelihood, bias correction, bias reduction. Throw in an OLS for shiggles

```{r}
fm = maxHLB ~ window*efficacy + maxT*efficacy
ols = lm(fm, data=df)
br.ml = betareg(fm, data=df, type="ML")
br.bc = betareg(fm, data=df, type="BC")
br.br = betareg(fm, data=df, type="BR")
```

Observe outputs
```{r}
summary(ols)
print(summary(br.ml))
summary(br.bc)
summary(br.br)
```
Check AIC/BIC
```{r}
scores = data.frame(Score=character(), OLS=numeric(), ML=numeric(), BR=numeric(), BC=numeric())
AIC = data.frame(Score="AIC", OLS=AIC(ols), ML=AIC(br.ml), BR=AIC(br.br), BC=AIC(br.bc))
BIC = data.frame(Score="BIC", OLS=BIC(ols), ML=BIC(br.ml), BR=BIC(br.br), BC=BIC(br.bc))
scores = rbind(scores,AIC,BIC)
print(scores)
```

Since bias reduction is best, let's construct a matrix of response transformed coefficients. Unsure of an easy way to do this
```{r}
tcoefs = data.frame(Base=character(), e65=character(), e75=character(), e85=character(), window=character(), maxT=character())

for (e in c(0.65,0.75,0.85)) {
  base = data.frame(window=60, efficacy=factor(e, levels=c(0.65,0.75,0.85)), maxT=1200)
  data.e65 = base
  data.e65[[2]] = factor(0.65, levels=c(0.65,0.75,0.85))
  data.e75 = base
  data.e75[[2]] = factor(0.75, levels=c(0.65,0.75,0.85))
  data.e85 = base
  data.e85[[2]] = factor(0.85, levels=c(0.65,0.75,0.85))
  data.window = base
  data.window[[1]] = 61
  data.maxT = base
  data.maxT[[3]] = 1201
  row = data.frame(Base=e, 
                   e65= -predict(br.br, base) + predict(br.br, data.e65),
                   e75=-predict(br.br, base) + predict(br.br, data.e75),
                   e85=-predict(br.br, base) + predict(br.br, data.e85),
                   window = -predict(br.br,base) + predict(br.br, data.window),
                   maxT = -predict(br.br, base) + predict(br.br, data.maxT)
                   )
  tcoefs=rbind(tcoefs,row)
}
print(tcoefs)
```

Stargazer tables


DF summary
```{r}
stargazer(as.data.frame(df %>% filter(efficacy==0.65) %>% select(maxHLB, maxT)), type="text",title="65% Efficacy", align=TRUE)
stargazer(as.data.frame(df %>% filter(efficacy==0.75) %>% select(maxHLB, maxT)), type="text",title="75% Efficacy", align=TRUE)
stargazer(as.data.frame(df %>% filter(efficacy==0.85) %>% select(maxHLB, maxT)), type="text",title="85% Efficacy", align=TRUE)

```
Comparing 3 models
```{r}
stargazer(ols, br.ml,br.bc,br.br, 
          type="latex",
          title="Regression output for Full Coordination In-Grove Spread Models",
          label="Tab:ExpectedValue-WindowPair-regressioncomparison",
          column.labels = c("OLS", "ML", "BC", "BR"),
          add.lines=list(
            c("AIC", round(AIC(ols),digits=5), round(AIC(br.ml),digits=5), round(AIC(br.bc),digits=5), round(AIC(br.br),digits=5)),
            c("BIC", round(BIC(ols),digits=5), round(BIC(br.ml),digits=5), round(BIC(br.bc),digits=5), round(BIC(br.br),digits=5))
            ),
          object.names=FALSE,
          model.names=FALSE,
          model.numbers=FALSE)
```

Coefficient table
```{r}
stargazer(tcoefs, summary=FALSE, type="text", rownames=FALSE, digits=7)
```

Now that it's log i think we have to graph it
```{r}
predictionData = data.frame(efficacy=numeric(), window=numeric(), maxT=numeric())
for (e in c(0.65,0.75,0.85)) {
  for (w in c(7,14,21,40,60,80,100)) {
    loopData = data.frame(efficacy=numeric(), window=numeric(), maxT=numeric())
    for (t in 1:1825) {
      data = data.frame(efficacy=e, window=w, maxT=t)
      loopData = rbind(loopData, data)
    }
    predictionData = rbind(predictionData,loopData)
  }
}
predictionData$efficacy = as.factor(predictionData$efficacy)
predictionData$maxHLB = predict(br.ml, predictionData)

```

```{r}
predictionData %>%
  mutate(window = as.factor(window), years=maxT/365) %>%
  ggplot(aes(x=maxT, y=maxHLB, color=efficacy, linetype=window)) +
  geom_line() +
  labs(x="Length of Infection", 
       y="Predicted Mean Severity",
       color="Efficacy",
       linetype="Window") +
  scale_y_continuous(breaks=seq(0,1,0.1)) +
  scale_color_viridis(discrete=TRUE, option="turbo") +
  theme_grey()
ggsave("windowpairs-output/predictedSpread.jpg", dpi=300, width=7, height=5)
```

yield curves?
```{r}
predictionData$yield = exp(-1.85*predictionData$maxHLB)
```

```{r}
predictionData %>%
  filter(maxT <= 1825) %>%
  mutate(window = as.factor(window), years=maxT/365) %>%
  ggplot(aes(x=maxT, y=yield, color=efficacy, linetype=window)) +
  geom_line() +
  labs(x="Length of Infection", y="Expected Yield", color="Efficacy", linetype="Window") +
  scale_y_continuous(breaks=seq(0,1,0.1)) +
  scale_color_viridis(discrete=TRUE, option="turbo") +
  theme_grey()
ggsave("windowpairs-output/predictedYield.jpg", dpi=300, width=7, height=5)
```
